---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Lindley"
date: "02/15/2021"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
#install.packages("wesanderson")
library(wesanderson)

```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
load("G:\\My Drive\\DataScience\\Lab_04\\data\\dennys.rda")
load("G:\\My Drive\\DataScience\\Lab_04\\data\\laquinta.rda")
```

### Exercise 1

```{r dennys_sum}
glimpse(dennys)
```
There are 1,643 observation and 6 columns. Each observation represents a particular dennys.

### Exercise 2

```{r laquinta_sum}
glimpse(laquinta)
```
There are 909 observations and 6 variables. Each observation is a particular la quinta.

### Exercise 3

There are no dennys outside the US. There are la quintas outside the US (Mexico, New Zealand, Honduras, Turkey, Chile, Columbia, and Canada). 

### Exercise 4

One way that might be complicated is determining the latitude and longitude limits of the united states and limiting the data set to just those that fit within those limits. Another way (and I think this is the one we're doing) is to have a list of the states and check to see if the state values of laquinta and dennys match that list. Any that don't are locations outside the united states.

### Exercise 5

```{r den_not_US}
dennys %>%
  filter(!(state %in% states$abbreviation))
```
This confirms what I saw on the website: no dennys outside the US.

### Exercise 6

```{r den_US}
dennys <- dennys %>%
  mutate(country = "United States")
```

### Exercise 7

```{r laq_not_US}
laquinta %>%
  filter(!(state %in% states$abbreviation))
```
Yes, I just spent the past hour trying to find the perfect data set of global postal codes to make a code to find country by postal code, and I failed to find one that was suitable. I'm settling for just googling it. Oh well. 

* AG = Mexico
* QR = Mexico
* CH = Mexico
* NL = Mexico
* ANT = Colombia
* ON = Canada
* VE = Mexico
* PU = Mexico
* SL = Mexico
* FM = Honduras
* BC = Canada 

### Exercise 8

```{r lq_country}
laquinta <- laquinta %>%
  mutate(country = case_when(
    state %in% state.abb     ~ "United States",
    state %in% c("AG", "QR", "CH", "NL", "VE", "PU", "SL") ~ "Mexico",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT"           ~ "Colombia",
    state == "FM"            ~ "Honduras"
  )) %>%
  filter(country == "United States")
``` 

### Exercise 9

```{r den_states}
dennys %>%
  count(state) %>%
  arrange(desc(n))
```

California has the most dennys (403). Delaware has the least number of dennys (1).

```{r lq_state}
laquinta %>%
  count(state) %>%
  arrange(desc(n))
```

Texas has the most la quintas (237) and Maine has the least number of la quintas (1). If Mitch Hedburg is right and la quintas and dennys were paired, I think you'd expect them to have the highest and lowest numbers in the same states.

### Exercise 10

```{r den_sq}
dennys %>%
  count(state) %>%
  inner_join(states, by = c("state" = "abbreviation")) %>%
  mutate(per_square_mile = n/(area/1000)) %>%
  arrange(desc(per_square_mile))
```
D.C. has the most dennys per thousand square miles (29.3). Alaska has the fewest dennys per thousand square mile (.005). This makes sense because D.C. is the smallest area on the list, which makes the denominator < 1. Also, Alaska is super large (I think it's the biggest state) and has very few dennys.


```{r lq_sq}
laquinta %>%
  count(state) %>%
  inner_join(states, by = c("state" = "abbreviation")) %>%
  mutate(per_square_mile = n/(area/1000)) %>%
  arrange(desc(per_square_mile))
```
Rhode island has the most la quintas per thousand square mile (1.3). The same reasoning as for D.C. above holds for Rhode Island. Alaska has the fewest la quintas per thousand square mile (0.003) because of the reason I gave above.

```{r estab}
dennys <- dennys %>%
  mutate(establishment = "Denny's")
laquinta <- laquinta %>%
  mutate(establishment = "La Quinta")
```

```{r combine}
dn_lq <- bind_rows(dennys, laquinta)
```

```{r all_plot}
ggplot(dn_lq, mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point() +
  labs(title = "Latitude and Longitude of Denny's and La Quintas", x = "Longitude (Decimal degrees)", y = "Latitude (Decimal degrees)") +
    scale_colour_grey(start = 0, end = .7) +
  theme_bw()
```

### Exercise 11

```{r NC}
dn_lq %>%
  filter(state == "NC") %>%
  ggplot(mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point(alpha = .6) +
  labs(title = "Latitude and Longitude of North Carolina Denny's and La Quintas", x = "Longitude (Decimal degrees)", y = "Latitude (Decimal degrees)") +
   scale_color_manual(values = wes_palette("BottleRocket2", n = 2))
```

While there are some la quintas that are near dennys (particularly between longitude -79 and -78 and around -81), there are la quintas not next to dennys. For example the point of 36.5 latitude is nowhere near a dennys. Even so, it seems to be more common for a la quinta to be near a dennys than not.


```{r TX}
dn_lq %>%
  filter(state == "TX") %>%
  ggplot(mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point(alpha = .4) +
  labs(title = "Latitude and Longitude of North Carolina Denny's and La Quintas", x = "Longitude (Decimal degrees)", y = "Latitude (Decimal degrees)") +
   scale_color_manual(values = wes_palette("BottleRocket2", n = 2))
```

The claim seems to be more true here. There are three main clusters of la quintas and dennys overlapping. Even outside the cluters, the la quinta and dennys points are close. There are some la quintas at the 35-36 latitude without dennys, but that is not as common as the two being paired. So, I think, generally, the Mitch Hedburg joke is true.