---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Lindley"
date: "02/15/2021"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
load("G:\\My Drive\\DataScience\\Lab_04\\data\\dennys.rda")
load("G:\\My Drive\\DataScience\\Lab_04\\data\\laquinta.rda")
```

### Exercise 1

```{r dennys_sum}
glimpse(dennys)
```
There are 1,643 observation and 6 columns. Each observation represents a particular dennys.

### Exercise 2

```{r laquinta_sum}
glimpse(laquinta)
```
There are 909 observations and 6 variables. Each observation is a particular la quinta.

### Exercise 3

There are no dennys outside the US. There are la quintas outside the US (Mexico, New Zealand, Honduras, Turkey, Chile, Columbia, and Canada). 

### Exercise 4

One way that might be complicated is determining the latitude and longitude limits of the united states and limiting the data set to just those that fit within those limits. Another way (and I think this is the one we're doing) is to have a list of the states and check to see if the state values of laquinta and dennys match that list. Any that don't are locations outside the united states.

### Exercise 5

...

### Exercise 6

...

Add exercise headings as needed.

