---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Lindley"
date: "02/15/2021"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
load("G:\\My Drive\\DataScience\\Lab_04\\data\\dennys.rda")
load("G:\\My Drive\\DataScience\\Lab_04\\data\\laquinta.rda")
```

### Exercise 1

```{r dennys_sum}
glimpse(dennys)
```
There are 1,643 observation and 6 columns. Each observation represents a particular dennys.

### Exercise 2

```{r laquinta_sum}
glimpse(laquinta)
```
There are 909 observations and 6 variables. Each observation is a particular la quinta.

### Exercise 3

There are no dennys outside the US. There are la quintas outside the US (Mexico, New Zealand, Honduras, Turkey, Chile, Columbia, and Canada)d and also say you're looking forward to working with them this summer

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

Add exercise headings as needed.

